---
title: "Alcohol vs Seat choice"
author: "Alexxis Ontiveros"
date: "spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot shows that the heavy drinkers are mostly seated in the back.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
People who sit in the back drink about three times as much as alcohol than the people in the front or the middle by a long shot.   



##Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is so small that it is un likely that the alcohol consumption in all three seats are the same.   


## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
The TukeyHSD plot shows the people in the back drink a lot more than people in the front; It shows the people in the middle drink less than the people in the back; The Middle-front shows no evidence of difference in the average alcohol consumption.   

## Conclusions

The evidence shows that most of the people that consume alcohol tend to sit in the back of the class


